Parsing Postfix log files

### 2009-02-24 doc/logparser-postfix-daemons.tex
Proofread postfix daemons appendix and made corrections/improvements.

% vim: set filetype=tex :
% Postfix components
\newglossaryentry{bounce}{name={bounce},type={postfix},description={
    The bounce daemon is responsible for sending bounce notifications in
    Postfix versions later than 2.2.  The definitive documentation is
    \url{http://www.postfix.org/bounce.8.html}.
}}

\newglossaryentry{cleanup}{name={cleanup},type={postfix},description={
    Cleanup processes all incoming mail after it has been accepted and
    before it is delivered.  It removes duplicate recipient addresses,
    inserts missing headers, and optionally rewrites addresses if
    configured to do so.  The definitive documentation is
    \url{http://www.postfix.org/cleanup.8.html}.
}}

\newglossaryentry{lmtp}{name={lmtp},type={postfix},description={
    Delivery of mail over \gls{LMTP} is performed by the lmtp component.
    The definitive documentation is
    \url{http://www.postfix.org/lmtp.8.html}.
}}

\newglossaryentry{local}{name={local},type={postfix},description={
    Local is the Postfix component responsible for local delivery of mail
    (i.e.\ delivered on the server Postfix is running on), whether it be to
    a user's mailbox or a program such as a mailing list manager or
    procmail (\url{http://www.procmail.org/}).  It also handles aliases and
    processing of a user's \texttt{.forward} file.  The definitive
    documentation is \url{http://www.postfix.org/local.8.html}.
}}

\newglossaryentry{pickup}{name={pickup},type={postfix},description={
    Pickup is the service that deals with mail submitted locally via
    postdrop and sendmail; it passes all submitted mail to cleanup.  The
    definitive documentation is \url{http://www.postfix.org/pickup.8.html}.
}}

\newglossaryentry{postdrop}{name={postdrop},type={postfix},description={
    Postdrop is used when submitting mail locally on the server: it creates
    a new mail in the queue and copies its input into the mail.  Subsequent
    delivery of the mail is the responsibility of other Postfix components.
    The definitive documentation is
    \url{http://www.postfix.org/postdrop.1.html}.
}}

\newglossaryentry{postsuper}{name={postsuper},type={postfix},description={
    Maintenance tasks such as deleting mails from the queue, putting mail
    on hold and later releasing it (no further delivery attempts will be
    made until it is released), and consistency checking of the mail queue.
    The definitive documentation is available at
    \url{http://www.postfix.org/postsuper.1.html}.
}}

\newglossaryentry{qmgr}{name={qmgr},type={postfix},description={
    Qmgr is the Postfix daemon that manages the mail queue, determining
    which mails will be delivered next.  Qmgr orders the mails based on the
    recipient for local mails and the destination server for remote
    addresses, ensuring that it balances the aims of achieving maximum
    concurrency while avoiding overwhelming destinations or wasting time
    and resources on non-responsive destinations.  The definitive
    documentation is \url{http://www.postfix.org/qmgr.8.html}.
}}

\newglossaryentry{sendmail}{name={sendmail},type={postfix},description={
    Postfix provides a command that is compatible with the Sendmail
    (\url{http://www.sendmail.org/}) mail submission program that all Unix
    commands that send mail depend on; it executes \daemon{postdrop} to
    place a new mail in the queue.  The definitive documentation is
    \url{http://www.postfix.org/sendmail.1.html}.
}}

\newglossaryentry{smtp}{name={smtp},type={postfix},description={
    Delivery of mail over \gls{SMTP} is performed by the smtp component.
    The definitive documentation is
    \url{http://www.postfix.org/smtp.8.html}.
}}

\newglossaryentry{smtpd}{name={smtpd},type={postfix},description={
    Smtpd is the Postfix program that accepts mail via \gls{SMTP}, and
    implements all the anti-spam restrictions Postfix provides.  The
    definitive documentation is \url{http://www.postfix.org/smtpd.8.html}.
}}

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    Virtual is the Postfix component responsible for delivery of mails to
    virtual domains.  With \daemon{local} delivery the destination is
    determined only by the portion of the email address on the left side of
    the @, whereas with \daemon{virtual} delivery the destination is
    determined by the entire email address.  E.g.\ if the server is
    responsible for both the \textbf{example.org} and \textbf{example.net}
    domains: \daemon{local} considers \textbf{john@example.org} and
    \textbf{john@example.net} to have the same mailbox, whereas
    \daemon{virtual} considers them to have different mailboxes.  Virtual
    delivery is used when a server hosts multiple domains where a username
    may be present in more than one domain but represent different users in
    each.  The definitive documentation is
    \url{http://www.postfix.org/virtual.8.html}.
}}

>>>>

% vim: set filetype=tex :
% Postfix components
\newglossaryentry{bounce}{name={bounce},type={postfix},description={
    The bounce daemon is responsible for sending bounce notifications in
    Postfix version 2.3 and later.
    \daemonDocURL{http://www.postfix.org/bounce.8.html}{2009/02/23}.
}}

\newglossaryentry{cleanup}{name={cleanup},type={postfix},description={
    The cleanup daemon processes all incoming mail after it has been
    accepted and before it is delivered.  It removes duplicate recipient
    addresses, inserts missing headers, and rewrites addresses if
    configured to do so.
    \daemonDocURL{http://www.postfix.org/cleanup.8.html}{2009/02/23}.
}}

\newglossaryentry{lmtp}{name={lmtp},type={postfix},description={
    Delivers mail using the \acronym{LMTP} protocol.
    \daemonDocURL{http://www.postfix.org/lmtp.8.html}{2009/02/23}.
}}

\newglossaryentry{local}{name={local},type={postfix},description={
    Local is the Postfix component responsible for local delivery of mail
    (i.e.\ mail delivered on the server Postfix is running on); this
    includes alias expansion, processing of a user's \texttt{.forward}
    file, and delivery of the mail, whether it be to a user's mailbox or a
    program such as a mailing list manager.
    \daemonDocURL{http://www.postfix.org/local.8.html}{2009/02/23}.
}}

\newglossaryentry{pickup}{name={pickup},type={postfix},description={
    Pickup is the daemon that deals with mail submitted locally via
    \daemon{postdrop} and \daemon{sendmail,} passing the mail on to
    \daemon{cleanup} for further processing.
    \daemonDocURL{http://www.postfix.org/pickup.8.html}{2009/02/23}.
}}

\newglossaryentry{postdrop}{name={postdrop},type={postfix},description={
    Postdrop is used when submitting mail locally on the server: it copies
    its input into a newly created mail in the queue, for processing by
    \daemon{pickup} and subsequent delivery by one or more of
    \daemon{lmtp}, \daemon{local}, \daemon{smtp}, or \daemon{virtual}.
    \daemonDocURL[\newline{}]{http://www.postfix.org/postdrop.1.html}{2009/02/23}.
}}

\newglossaryentry{postsuper}{name={postsuper},type={postfix},description={
    Used by the administrator for maintenance tasks such as deleting mails
    from the queue, putting mail on hold and later releasing it, and
    consistency checking of the mail queue.
    \daemonDocURL[\newline{}]{http://www.postfix.org/postsuper.1.html}{2009/02/23}.
}}

\newglossaryentry{qmgr}{name={qmgr},type={postfix},description={
    Qmgr is the Postfix daemon that manages the mail queue, determining
    which mails will be delivered next.  Qmgr groups mail based on the
    recipient for local mails and the destination server for remote
    addresses, ensuring that it achieves maximum concurrency without
    overwhelming destinations or wasting resources on non-responsive
    destinations.
    \daemonDocURL{http://www.postfix.org/qmgr.8.html}{2009/02/23}.
}}

\newglossaryentry{sendmail}{name={sendmail},type={postfix},description={
    A Postfix component that is compatible with the Sendmail
    (\urlLastCheckedNoParens{http://www.sendmail.org/}{2009/02/23}) mail
    submission program which all Unix commands that need to send mail use;
    it executes \daemon{postdrop} to place a new mail in the queue.
    \daemonDocURL[\newline{}]{http://www.postfix.org/sendmail.1.html}{2009/02/23}.
}}

\newglossaryentry{smtp}{name={smtp},type={postfix},description={
    Delivers mail using the \acronym{SMTP} protocol.
    \daemonDocURL{http://www.postfix.org/smtp.8.html}{2009/02/23}.
}}

\newglossaryentry{smtpd}{name={smtpd},type={postfix},description={
    The Postfix component that accepts mail via \acronym{SMTP}, and
    implements most of the anti-spam restrictions Postfix provides.
    \daemonDocURL{http://www.postfix.org/smtpd.8.html}{2009/02/23}.
}}

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    The Postfix component responsible for delivery of mails to virtual
    domains.  When \daemon{local} delivers mail the destination is
    determined only by the portion of the email address on the left side of
    the \texttt{@}, whereas with \daemon{virtual} delivery the destination
    is determined by the entire email address.  E.g.\ if the server is
    responsible for both the \texttt{example.org} and \texttt{example.net}
    domains: \daemon{local} would deliver mail for
    \texttt{john@example.org} and \texttt{john@example.net} to the same
    mailbox, whereas \daemon{virtual} would deliver mail for those
    addresses to different mailboxes.  Virtual delivery is used where the
    local part of an address may be present in multiple domains, and each
    must be delivered to different users.
    \daemonDocURL{http://www.postfix.org/virtual.8.html}{2009/02/23}.
}}
